\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-11-12 paper.tex
replaced three tables with an all-in-one

@@

Tables \ref{tbl:manual} and \ref{tbl:generated} show the collected data for the
manual and the generated implementation. They present the base case in absolute
values and the implementations with the ID algorithms relative to that base
case.

\begin{table}[H]
  \centering
  \begin{tabular}{lrrrr}
  \hline
      & base & watchdog & reputation & both\\
  \hline
  size (bytes) & 10500 & 148\% & 127\% & 175\%\\
  frames & 20 & 255\% & 160\% & 315\%\\
  bytes & 476 & 406\% & 181\% & 487\%\\
  time ($\mu$s) & 48 & 196\% & 183\% & 310\%\\
  \hline
  \end{tabular}
  \caption{Results for the manual implementation.}
  \label{tbl:manual}
\end{table}

\begin{table}[H]
  \centering
  \begin{tabular}{lrrrr}
  \hline
         & base & watchdog & reputation & both\\
  \hline
  size (bytes) & 10496 & 175\% & 156\% & 200\%\\
  frames & 20 & 245\% & 160\% & 275\%\\
  bytes & 476 & 399\% & 186\% & 454\%\\
  time ($\mu$s) & 48 & 252\% & 252\% & 288\%\\
  \hline
  \end{tabular}
  \caption{Results for the generated implementation.}
  \label{tbl:generated}
\end{table}

@@

Table \ref{tbl:summary} compares the two situations by subtracting the manual
case from the generated case, showing the impact of the code generation. A
relative value for the entire implementation with both algorithms is also
presented.

\begin{table}[H]
  \centering
  \begin{tabular}{lrrrrr}
  \hline
                & base & watchdog & reputation & both  & result \\
  \hline
  size (bytes)  & -4    & 2822     & 3070       & 2664  & 115\%  \\
  frames        & 0     & -2       & 0          & -8    & 87\%   \\
  bytes         & 0     & -36      & 24         & -156  & 93\%   \\
  time ($\mu$s) & 0     & 27       & 33         & -11   & 93\%   \\
  \hline
  \end{tabular}
  \caption{Comparison of both manual and generated implementations.}
  \label{tbl:summary}
\end{table}

>>>>

\begin{table*}[b]
  \centering
  \bgroup
  \def\arraystretch{1.3}
  \begin{tabular}{llrrrrrrr}
\toprule
              &            & base  & \multicolumn{2}{c}{watchdog} & \multicolumn{2}{c}{reputation} & \multicolumn{2}{c}{both} \\
\midrule
size (bytes)  & manual     & 10466 & 15530 &  +48\% & 13306 &  +27\% & 18334 &  +75\%\\
              & generated  & 10466 & 18352 &  +75\% & 16376 &  +56\% & 20998 & +101\%\\
\cline{2-9}
              & difference &     0 &  2822 &  +18\% &  3070 &  +23\% &  2664 &  +15\%\\
\hline
packets sent  & manual     &    20 &    51 & +155\% &    32 &  +60\% &    63 & +215\%\\
              & generated  &    20 &    49 & +145\% &    32 &  +60\% &    55 & +175\%\\
\cline{2-9}
              & difference &     0 &    -2 &   -4\% &     0 &   0\% &    -8 &   -13\%\\
\hline
bytes sent    & manual     &   476 &  1933 & +306\% &   860 &  +81\% &  2317 & +387\%\\
              & generated  &   476 &  1897 & +299\% &   884 &  +86\% &  2161 & +354\%\\
\cline{2-9}
              & difference &     0 &   -36 &   -2\% &    24 &   +3\% &  -156 &   -7\%\\
\hline
execution
time ($\mu$s) & manual     &    48 &    94 &  +96\% &    88 &  +83\% &   149 & +210\%\\
              & generated  &    48 &   121 & +152\% &   121 & +152\% &   138 & +188\%\\
\cline{2-9}
              & difference &     0 &    27 &  +29\% &    33 &  +38\% &   -11 &   -7\%\\
\bottomrule
  \end{tabular}
  \egroup
  \caption{Results and Side-by-Side Comparison.}
  \label{tbl:results}
\end{table*}

@@

Table \ref{tbl:results} shows the collected data for the manual and the
generated implementation, as well as a comparison in absolute values and
relative.

@@

Table \ref{tbl:results} also compares the two situations by subtracting the
manual case from the generated case, showing the impact of the code generation.
A relative value for this difference, to the manual case, is also included.
